---
title: "erinsplots_gg"
editor: source
---

# Input for/from Erin's work



<!--
`gwwc_text_clicks`: Observations of link clicks ... by texts above video `gwwc_vid_clicks`: ... by video content


(We focus on the email results because we expect the 'clicks' are less meaningful.)

`gwwc_text_results`: Observations of emails provided ... by texts above video

-->

`gwwc_vid_results`: Observations of emails provided... by video content

<!-- The files:

`textdata_dv_linkclicks.csv`, `videodata_dv_results.csv`, `textdata_dv_results.csv` , and `videodata_dv_linkclicks.csv`

are gitignored because of size. -->

:::

```{r input_gwwc_vid_results_old_ver, eval=false}

#source(here("gwwc", "giving_guides", "input_build_gwwc_gg_data_results.R"))

#source(here("gwwc", "giving_guides", "input_build_gwwc_gg_data_clicks.R"))
source(here("gwwc", "giving_guides", "clean_gg_data.R")) #a function for some specific cleaning steps

gwwc_vid_results <-  read.csv(here(raw_data_path, "videodata_dv_results.csv"))
gwwc_vid_results <- clean_gwwc_gg(gwwc_vid_results)

#videos
#print(data %>% group_by(Video) %>% summarise(n=n(),cost=mean(ave.cost.impr)*100),n=50)

gwwc_vid_results <-  gwwc_vid_results %>% vid_clean

gwwc_vid_results$media <- factor( gwwc_vid_results$media , ordered = FALSE )
gwwc_vid_results$media <- relevel( gwwc_vid_results$media, ref="factual short")

#print(data %>% group_by(Video,media) %>% summarise(n=n(),cost=mean(ave.cost.impr)*100),n=50)

##cost adjusted DV
gwwc_vid_results <- gwwc_vid_results %>% mutate(DV_costadj= DV/ave.cost.impr)

```


# Plots from Erin

### PLOT: Cost adjusted DV (results) by video


### PLOT: DV (Results) by video

```{r}


gwwc_vid_results %>%
   grpsumgg(media, DV, .1) %>%
  ggplot(aes(x=media, y=mean_dv)) +
  geom_bar(stat='identity', fill="#0072B2",position=dodge) +
  ylab('Results (%)')+
  xlab('Video')+
  ggtitle('Results by Video')+
  scale_x_discrete(labels=vid_types)



```

### PLOT: Cost adjusted DV (results) by video and audience

^[Questions/Notes: Removed the retargeting audience]

```{r}

#print(gwwc_vid_results %>% filter(ave.cost.impr>0 & audience !="retargeting") %>% group_by(media,audience) %>% #summarise(results=mean(DV_costadj),SE=std.error(DV_costadj),n=n()),n=50) %>% .kable(digits=2)


gwwc_vid_results %>% filter(ave.cost.impr>0 & audience !="retargeting") %>%
  group_by(media, audience) %>%
  summarise(mean_dv = mean(DV_costadj, na.rm=TRUE),
            se_dv = sd(DV_costadj, na.rm=TRUE)/sqrt(n())) %>%
  ggplot(aes(x=audience, y=mean_dv, group=media, fill=media)) +
  gg_gg_options +
  labs(fill="Video")+
  scale_fill_brewer(palette="RdBu")+
  ylab('Results/$ spent')+
  xlab('Audience')+
  ggtitle('Results/$ spent by Video and Audience')+
  theme_apa(legend.font.size = 8,legend.use.title = TRUE)+
  scale_y_continuous(limits = c(0,.25), oob = rescale_none, breaks=seq(0,.75, by=.25)) +
  scale_x_discrete(labels=c("philanthropy","animal","climate","general","lookalike","poverty","retargeting"))
#levels(gwwc_vid_results$audience)


```

### PLOT: DV (results) by video and audience

Questions/Notes: Removed the retargeting audience

```{r}


gwwc_vid_results %>% filter(ave.cost.impr > 0 &
    audience != "retargeting") %>% group_by(media, audience) %>% summarise(
      results = 100 * mean(DV),
      SE = 100 * std.error(DV),
      n = n()
    ) %>% .kable(digits = 2) %>% .kable_styling()


gwwc_vid_results %>% filter(ave.cost.impr>0 & audience !="retargeting") %>%
  group_by(media, audience) %>%
  summarise(mean_dv = 100*mean(DV, na.rm=TRUE),
            se_dv = 100*sd(DV, na.rm=TRUE)/sqrt(n())) %>%
  ggplot(aes(x=audience, y=mean_dv, group=media, fill=media)) +
  gg_gg_options +
  labs(fill="Video")+
  scale_fill_brewer(palette="RdBu")+
  ylab('Results (%)')+
  xlab('Audience')+
  ggtitle('Results by Video and Audience')+
  theme_apa(legend.font.size = 8,legend.use.title = TRUE)+
  scale_y_continuous(limits = c(0,1.1),  oob = rescale_none,  breaks=seq(0,1.1, by=.1)) +
  scale_x_discrete(labels=c("philanthropy","animal","climate","general","lookalike","poverty","retargeting"))




```

### PLOT: Cost adjusted DV (results) by audience

```{r}
#pirint(gwwc_vid_results %>% filter(ave.cost.impr>0 & audience !="retargeting") %>% group_by(audience) %>% summarise(results=mean(DV_costadj),SE=std.error(DV_costadj),n=n()),n=50)

```

```{r}

gwwc_vid_results %>% filter(ave.cost.impr>0 & audience !="retargeting") %>%
  group_by(audience) %>%
summarise(mean_dv = mean(DV_costadj, na.rm=TRUE),
            se_dv = sd(DV_costadj, na.rm=TRUE)/sqrt(n())) %>%
  ggplot(aes(x=audience, y=mean_dv)) +
  gg_gg_options +
  ylab('Results/$ spent')+
  xlab('Audience')+
  ggtitle('Results/$ spent by Audience')+
  scale_y_continuous(limits = c(0,.2),  breaks=seq(0,.2, by=.05)) +
  scale_x_discrete(labels=c("philanthropy","animal"   ,"climate","general","lookalike","poverty"))


```

### PLOT: DV (Results) by audience

```{r}
#print(gwwc_vid_results %>% filter(ave.cost.impr>0 & audience !="retargeting") %>% group_by(audience) %>% summarise(results=100*mean(DV),SE=100*std.error(DV),n=n()),n=50)


gwwc_vid_results %>% filter(ave.cost.impr>0 & audience !="retargeting") %>%
  group_by(audience) %>%
  summarise(mean_dv = 100*mean(DV, na.rm=TRUE),
            se_dv = 100*sd(DV, na.rm=TRUE)/sqrt(n())) %>%
  ggplot(aes(x=audience, y=mean_dv)) +
  gg_gg_options +
  ylab('Results (%)')+
  xlab('Audience')+
  ggtitle('Results by Audience')+
  scale_y_continuous(limits = c(0,.4),  breaks=seq(0,.4, by=.05)) +
  scale_x_discrete(labels=c("philanthropy","animal"   ,"climate","general","lookalike","poverty"))

```

### PLOT: Cost adjusted DV (results) by age and gender

^[Did not filter out the retargeting audience like i did for the other charts]

```{r}
gwwc_vid_results$Gender <- as.factor(gwwc_vid_results$Gender)
#levels(gwwc_vid_results$Gender)

class(gwwc_vid_results$Age)
gwwc_vid_results$Age <- relevel(gwwc_vid_results$Age, ref="18-24")
#levels(gwwc_vid_results$Age)

#print(gwwc_vid_results %>% filter(ave.cost.impr>0) %>% group_by(Age,Gender) %>% summarise(results=mean(DV_costadj),SE=std.error(DV_costadj),n=n()),n=50)


gwwc_vid_results %>% filter(ave.cost.impr>0 & Age!="13-17") %>%
  group_by(Age, Gender) %>%
  summarise(mean_dv = mean(DV_costadj, na.rm=TRUE),
            se_dv = sd(DV_costadj, na.rm=TRUE)/sqrt(n())) %>%
  ggplot(aes(x=Age, y=mean_dv, group=Gender, fill=Gender)) +
  gg_gg_options +
  labs(fill="Gender")+
  scale_fill_brewer(palette="Paired")+
  ylab('Results/$ spent')+
  xlab('Age')+
  ggtitle('Results/$ spent by Age and Gender')+
  theme_apa(legend.font.size = 8,legend.use.title = TRUE)+
  scale_y_continuous(limits = c(0,.35),  breaks=seq(0,.35, by=.1)) +
  scale_x_discrete(labels=c("18-24","25-34","35-44","45-54","55-64","65+" ))

```

### PLOT: DV (results) gggender

```{r}
gwwc_vid_results$Gender <- as.factor(gwwc_vid_results$Gender)
#levels(gwwc_vid_results$Gender)

#class(gwwc_vid_results$Age)
gwwc_vid_results$Age <- relevel(gwwc_vid_results$Age, ref="18-24")
gwwc_vid_results$Age <- relevel(gwwc_vid_results$Age, ref="13-17")
#levels(gwwc_vid_results$Age)

#print(gwwc_vid_results %>% filter(ave.cost.impr>0) %>% group_by(Age,Gender) %>% summarise(results=100*mean(DV),SE=std.error(100*DV),n=n()),n=50)

gwwc_vid_results %>% filter(ave.cost.impr>0 & Age!="13-17") %>%
  group_by(Age, Gender) %>%
  summarise(mean_dv = 100*mean(DV, na.rm=TRUE),
            se_dv = 100*sd(DV, na.rm=TRUE)/sqrt(n())) %>%
  ggplot(aes(x=Age, y=mean_dv, group=Gender, fill=Gender)) +
  gg_gg_options +
  labs(fill="Gender")+
  scale_fill_brewer(palette="Paired")+
  ylab('Results (%)')+
  xlab('Age')+
  ggtitle('Results by Age and Gender')+
  theme_apa(legend.font.size = 8,legend.use.title = TRUE)+
  scale_y_continuous(limits = c(0,.75),  breaks=seq(0,.75, by=.25)) +
  scale_x_discrete(labels=c("18-24","25-34","35-44","45-54","55-64","65+" ))

```

### PLOT: Cost adjusted DV (results) by Video and Age

```{r}
class(gwwc_vid_results$Age)
gwwc_vid_results$Age <- relevel(gwwc_vid_results$Age, ref="18-24")
gwwc_vid_results$Age <- relevel(gwwc_vid_results$Age, ref="13-17")
levels(gwwc_vid_results$Age)

#print(gwwc_vid_results %>% filter(ave.cost.impr>0) %>% group_by(Age,media) %>% summarise(results=mean(DV_costadj),SE=std.error(DV_costadj),n=n()),n=50)


gwwc_vid_results %>% filter(ave.cost.impr>0 & Age!="13-17") %>%
  group_by(media, Age) %>%
  summarise(mean_dv = mean(DV_costadj, na.rm=TRUE),
            se_dv = sd(DV_costadj, na.rm=TRUE)/sqrt(n())) %>%
  ggplot(aes(x=Age, y=mean_dv, group=media, fill=media)) +
  gg_gg_options +
  labs(fill="Video")+
  scale_fill_brewer(palette="RdBu")+
  ylab('Results/$ spent')+
  xlab('Age')+
  ggtitle('Results/$ spent by Video and Age')+
  theme_apa(legend.font.size = 8,legend.use.title = TRUE)+
  scale_y_continuous(limits = c(0,.2),  breaks=seq(0,.2, by=.05)) +
  scale_x_discrete(labels=c("18-24","25-34","35-44","45-54","55-64","65+"))


```

### PLOT: DV (results) by video and age

```{r}
class(gwwc_vid_results$Age)
gwwc_vid_results$Age <- relevel(gwwc_vid_results$Age, ref="18-24")
gwwc_vid_results$Age <- relevel(gwwc_vid_results$Age, ref="13-17")
#levels(gwwc_vid_results$Age)

gwwc_vid_results %>% filter(ave.cost.impr>0) %>% group_by(Age,media) %>% summarise(results=100*mean(DV),SE=100*std.error(DV),n=n()) %>%
  .kable(digits=2) %>%  .kable_styling()

```

```{r}



gwwc_vid_results %>% filter(ave.cost.impr>0 & Age !="13-17") %>%
    group_by(media, Age) %>%
  summarise(mean_dv = 100*mean(DV, na.rm=TRUE),
            se_dv = 100*sd(DV, na.rm=TRUE)/sqrt(n())) %>%
  ggplot(aes(x=Age, y=mean_dv, group=media, fill=media)) +
  gg_gg_options +
  labs(fill="Video")+
  scale_fill_brewer(palette="RdBu")+
  ylab('Results (%)')+
  xlab('Age')+
  ggtitle('Results by Video and Age')+
  theme_apa(legend.font.size = 8,legend.use.title = TRUE)+
  scale_y_continuous(limits = c(0,.85),  breaks=seq(0,.85, by=.25)) +
  scale_x_discrete(labels=c("18-24","25-34","35-44","45-54","55-64","65+"))


```

## Erin's proposed models


### Regressions with interactions

```{r}
#lm(data = gwwc_vid_results, DV~Gender*Age+ave.cost.impr)
#lm(data = gwwc_vid_results,DV~Gender*Age))

```

### Regressions with no interactions

just demographics, not control

```{r}
#data = lm(gwwc_vid_results,DV~Gender+Age)
```

just demographic, controlling for cost

```{r}
#lm(gwwc_vid_results,DV~Gender+Age+ave.cost.impr)

```

means and standard errors for age groups/gender

```{r}
gwwc_vid_results %>% group_by(Gender,Age) %>% summarise(results=mean(DV)*100,SE=std.error(DV)*100,n=n(),cost=mean(ave.cost.impr),CPR=cost/results) %>%
  .kable() %>% .kable_styling()
```

```{r}

hist(gwwc_vid_results$DV_costadj[gwwc_vid_results$DV_costadj>0])
hist(gwwc_vid_results$DV_costadj[gwwc_vid_results$DV_costadj>=0])
```

### DEMOGRAPHICS WITH CONTROLS FOR VIDEO AND COST

```{r}


#lm(gwwc_vid_results,DV~Gender+Age+ave.cost.impr)
#lm(gwwc_vid_results, DV_costadj~Gender+Age)
```

#### AUDIENCES

main effects

```{r}
#lm(gwwc_vid_results,DV~Gender+Age+ave.cost.impr+audience)
```

NEW DV

```{r}
#lm(gwwc_vid_results,DV_costadj~Gender+Age+audience)

  #interactions
  #lm(gwwc_vid_results,DV~Gender*audience+ave.cost.impr+Age)

## NEW DV
    #lm(gwwc_vid_results,DV_costadj~Gender*audience+Age)
  #lm(gwwc_vid_results,DV~Age*audience+ave.cost.impr+Gender)

  #means for audience
gwwc_vid_results %>%
  group_by(audience) %>%
  summarise(
    results=mean(DV)*100,
    SE=std.error(DV)*100,
    n=n(),
    cost=mean(ave.cost.impr),
    CPR=cost/results) %>%
    .kable %>%
      .kable_styling()

```

#### MESSAGES

no controls

```{r}
#lm(gwwc_vid_results,DV~message
  #control for cost only
  #lm(gwwc_vid_results,DV~message+ave.cost.impr)
  #check results with campaign
  #lm(gwwc_vid_results,DV~Campaign.name)
  #check results with campaign and cost control
  #lm(gwwc_vid_results,DV~Campaign.name+ave.cost.impr)
```

with controls

```{r}
#lm(gwwc_vid_results,DV~Gender+Age+ave.cost.impr+audience+message)

#interactions
#with audience
#lm(gwwc_vid_results,DV~message*audience+ave.cost.impr+Age+Gender)
#with Gender
#lm(gwwc_vid_results,DV~message*Gender+ave.cost.impr+Age+audience)
#with Age (emotional much worse with ages 65+)
#lm(gwwc_vid_results,DV~message*Age+ave.cost.impr+Age+audience)

```

interaction with age and campaign restriction

```{r}

#lm(gwwc_vid_results,DV~message*agetrin+message*restriction18_39+ave.cost.impr+Age+Gender)
#lm(gwwc_vid_results,DV~message*agetrin+message*restriction18_39+ave.cost.impr)


```

in just early campaigns

```{r}
#lm(subset(data,restriction18_39==0),DV~message*agetrin+ave.cost.impr)


```

### MEDIA

no controls

```{r}
#lm(gwwc_vid_results,DV~media)

```

means and SEs

```{r}
gwwc_vid_results %>% group_by(media) %>% summarise(results=mean(DV)*100,SE=std.error(DV)*100,n=n(),cost=mean(ave.cost.impr),CPR=cost/results)

```

control for cost only

```{r}
#lm(gwwc_vid_results,DV~media+ave.cost.impr)
```

## NEW DV

```{r}
#lm(gwwc_vid_results,DV_costadj~media))####THIS IS GOOD

```

with controls

```{r}
#lm(gwwc_vid_results,DV~Gender+Age+ave.cost.impr+audience+media)
```

### NEW DV

```{r}
#lm(gwwc_vid_results,DV_costadj~Gender+Age+audience+media)

```

interactions

```{r}
#lm(gwwc_vid_results,DV~media*Age+media*Gender+media*audience+ave.cost.impr)
#lm(gwwc_vid_results,DV_costadj~media*Age+media*Gender+media*audience)
#lm(gwwc_vid_results,DV~media*Age+media*Gender+media*audience)
#lm(gwwc_vid_results,DV_costadj~Age+Gender+media*audience)

```

with audience

```{r}
#lm(gwwc_vid_results,DV~media*audience+ave.cost.impr+Age+Gender)
```
z
### Regressions with interactions

```{r}
#lm(data = gwwc_vid_results, DV~Gender*Age+ave.cost.impr)
#lm(data = gwwc_vid_results,DV~Gender*Age))

```

### Regressions with no interactions

just demographics, not control

```{r}
#data = lm(gwwc_vid_results,DV~Gender+Age)
```

just demographic, controlling for cost

```{r}
#lm(gwwc_vid_results,DV~Gender+Age+ave.cost.impr)

```

means and standard errors for age groups/gender

```{r}
gwwc_vid_results %>% group_by(Gender,Age) %>% summarise(results=mean(DV)*100,SE=std.error(DV)*100,n=n(),cost=mean(ave.cost.impr),CPR=cost/results) %>%
  .kable() %>% .kable_styling()
```

```{r}

hist(gwwc_vid_results$DV_costadj[gwwc_vid_results$DV_costadj>0])
hist(gwwc_vid_results$DV_costadj[gwwc_vid_results$DV_costadj>=0])
```

### DEMOGRAPHICS WITH CONTROLS FOR VIDEO AND COST

```{r}


#lm(gwwc_vid_results,DV~Gender+Age+ave.cost.impr)
#lm(gwwc_vid_results, DV_costadj~Gender+Age)
```

#### AUDIENCES

main effects

```{r}
#lm(gwwc_vid_results,DV~Gender+Age+ave.cost.impr+audience)
```

NEW DV

```{r}
#lm(gwwc_vid_results,DV_costadj~Gender+Age+audience)

  #interactions
  #lm(gwwc_vid_results,DV~Gender*audience+ave.cost.impr+Age)

## NEW DV
    #lm(gwwc_vid_results,DV_costadj~Gender*audience+Age)
  #lm(gwwc_vid_results,DV~Age*audience+ave.cost.impr+Gender)

  #means for audience
gwwc_vid_results %>%
  group_by(audience) %>%
  summarise(
    results=mean(DV)*100,
    SE=std.error(DV)*100,
    n=n(),
    cost=mean(ave.cost.impr),
    CPR=cost/results) %>%
    .kable %>%
      .kable_styling()

```

#### MESSAGES

no controls

```{r}
#lm(gwwc_vid_results,DV~message
  #control for cost only
  #lm(gwwc_vid_results,DV~message+ave.cost.impr)
  #check results with campaign
  #lm(gwwc_vid_results,DV~Campaign.name)
  #check results with campaign and cost control
  #lm(gwwc_vid_results,DV~Campaign.name+ave.cost.impr)
```

with controls

```{r}
#lm(gwwc_vid_results,DV~Gender+Age+ave.cost.impr+audience+message)

#interactions
#with audience
#lm(gwwc_vid_results,DV~message*audience+ave.cost.impr+Age+Gender)
#with Gender
#lm(gwwc_vid_results,DV~message*Gender+ave.cost.impr+Age+audience)
#with Age (emotional much worse with ages 65+)
#lm(gwwc_vid_results,DV~message*Age+ave.cost.impr+Age+audience)

```

interaction with age and campaign restriction

```{r}

#lm(gwwc_vid_results,DV~message*agetrin+message*restriction18_39+ave.cost.impr+Age+Gender)
#lm(gwwc_vid_results,DV~message*agetrin+message*restriction18_39+ave.cost.impr)


```

in just early campaigns

```{r}
#lm(subset(data,restriction18_39==0),DV~message*agetrin+ave.cost.impr)


```

### MEDIA

no controls

```{r}
#lm(gwwc_vid_results,DV~media)

```

means and SEs

```{r}
gwwc_vid_results %>% group_by(media) %>% summarise(results=mean(DV)*100,SE=std.error(DV)*100,n=n(),cost=mean(ave.cost.impr),CPR=cost/results)

```

control for cost only

```{r}
#lm(gwwc_vid_results,DV~media+ave.cost.impr)
```

## NEW DV

```{r}
#lm(gwwc_vid_results,DV_costadj~media))####THIS IS GOOD

```

with controls

```{r}
#lm(gwwc_vid_results,DV~Gender+Age+ave.cost.impr+audience+media)
```

### NEW DV

```{r}
#lm(gwwc_vid_results,DV_costadj~Gender+Age+audience+media)

```

interactions

```{r}
#lm(gwwc_vid_results,DV~media*Age+media*Gender+media*audience+ave.cost.impr)
#lm(gwwc_vid_results,DV_costadj~media*Age+media*Gender+media*audience)
#lm(gwwc_vid_results,DV~media*Age+media*Gender+media*audience)
#lm(gwwc_vid_results,DV_costadj~Age+Gender+media*audience)

```

with audience

```{r}
#lm(gwwc_vid_results,DV~media*audience+ave.cost.impr+Age+Gender)
```

## More models and crosstabs


Means and SEs

```{r}

gwwc_vid_results %>% group_by(audience,media) %>% summarise(results=mean(DV)*100,SE=std.error(DV)*100,n=n(), cost=mean(ave.cost.impr),CPR=cost/results) %>%
.kable() %>% .kable_styling()

```

with Gender

```{r}
#lm(gwwc_vid_results,DV~media*Gender+ave.cost.impr+Age+audience)
```

means and SEs

```{r, eval=FALSE}

gwwc_vid_results %>% group_by(Gender, media) %>% summarise(
  results = mean(DV) * 100,
  SE = std.error(DV) * 100,
  n = n(),
  cost = mean(ave.cost.impr),
  CPR = cost / results
)

```

```{=html}
<!--
with Age (emotional much worse with ages 65+)

#lm(gwwc_vid_results,DV~media*Age+ave.cost.impr+Age+audience)


means and SEs
print(gwwc_vid_results %>% group_by(Age,media) %>% summarise(results=mean(DV)*100,SE=std.error(DV)*100,n=n(),cost=mean(ave.cost.impr),CPR=cost/results),n = 50)
print(gwwc_vid_results %>% group_by(audience,Age,media) %>% summarise(results=mean(DV)*100,SE=std.error(DV)*100,n=n(),cost=mean(ave.cost.impr),CPR=cost/results),n = 500)
-->
```
interaction with age and campaign restriction - old people really hated factual long

```{r}
#lm(gwwc_vid_results,DV~media*agetrin+media*restriction18_39+ave.cost.impr+Age+Gender))
#lm(gwwc_vid_results,DV~media*agetrin+media*restriction18_39+ave.cost.impr))
```

in just early campaigns

```{r}
#subset(gwwc_vid_results,restriction18_39==0),DV~media*agetrin+ave.cost.impr))
```

means and SEs

```{r, eval=FALSE}

gwwc_vid_results %>% filter(restriction18_39 == 0) %>% group_by(Age, media) %>% summarise(
  results = mean(DV) * 100,
  SE = std.error(DV) * 100,
  n = n(),
  cost = mean(ave.cost.impr),
  CPR = cost / results
)


```

# DEMOGRPAHICS AND COST ONLY

regressions with interactions

```{r}
#lm(gwwc_vid_results,DV_costadj~Gender*Age)) #no significant effects

```

regressions with no interactions just demographic, not control

```{r}
#lm(gwwc_vid_results,DV_costadj~Gender+Age))

```

means and standard errors for age groups/gender

```{r}
print(gwwc_vid_results %>% group_by(Gender,Age) %>% summarise(results=mean(DV_costadj)*100,SE=std.error(DV_costadj)*100,n=n()),n=50) ##idk if the changes i made to this line make sense


```

#### DEMOGRAPHICS WITH CONTROLS FOR VIDEO

```{r}
#gwwc_vid_results %>% lm(data = ., DV_costadj~Gender+Age+Video))

```

#### AUDIENCES

main effects

```{r}
#lm(gwwc_vid_results,DV_costadj~Gender+Age+audience))

```

interactions

```{r}
#lm(gwwc_vid_results,DV_costadj~Gender*audience+Age))
#lm(gwwc_vid_results,DV_costadj~Age*audience+Gender))

```

means for audience

```{r, eval=FALSE}

gwwc_vid_results %>% group_by(audience) %>%
  summarise(
  results = mean(DV_costadj) * 100,
  SE = std.error(DV_costadj) * 100,
  n = n()
)

#Why all NaN?


```

#### MESSAGES

no controls

```{r}
#lm(gwwc_vid_results,DV_costadj~message))
#lm(gwwc_vid_results,DV~message+ave.cost.impr))
```

check results with campaign

```{r}
#lm(gwwc_vid_results,DV_costadj~Campaign.name))
```

with controls

```{r}
#lm(gwwc_vid_results,DV_costadj~Gender+Age+audience+message))

```

interactions with audience

```{r}
#lm(gwwc_vid_results,DV_costadj~message*audience+Age+Gender))
```

with Gender

```{r}
#lm(gwwc_vid_results,DV_costadj~message*Gender+Age+audience))
```

with Age (emotional much worse with ages 65+)

```{r}
#lm(gwwc_vid_results,DV_costadj~message*Age+Age+audience))

```

interaction with age and campaign restriction

```{r}
#lm(gwwc_vid_results,DV_costadj~message*agetrin+message*restriction18_39+Age+Gender))
#lm(gwwc_vid_results,DV_costadj~message*agetrin+message*restriction18_39))
```

in just early campaigns

```{r}
#lm(subset(gwwc_vid_results,restriction18_39==0),DV_costadj~message*agetrin))

```

#### MEDIA

no controls

```{r}
#lm(gwwc_vid_results,DV_costadj~media))

```

means and SEs

```{r}

gwwc_vid_results %>%
  filter(ave.cost.impr > 0) %>% group_by(media) %>% summarise(
  mean(DV_costadj),
  results = mean(DV) * 100,
  SE = std.error(DV) * 100,
  n = n(),
  cost = mean(ave.cost.impr),
  CPR = cost / results,
  RPC = results / cost
) ##idk how to do this line?

```

with controls

```{r}
#lm(gwwc_vid_results,DV_costadj~Gender+Age+audience+media))

```

interactions

```{r}
#lm(gwwc_vid_results,DV_costadj~media*Age+media*Gender+media*audience))

```

with audience

```{r}
#lm(gwwc_vid_results,DV_costadj~media*audience+Age+Gender))

```

means and SEs

```{r, eval=FALSE}

gwwc_vid_results %>% group_by(audience, media) %>% summarise(
  results = mean(DV) * 100,
  SE = std.error(DV) * 100,
  n = n(),
  cost = mean(ave.cost.impr),
  CPR = cost / results
) ###skipped updating

```

with Gender

```{r}
#lm(gwwc_vid_results,DV_costadj~media*Gender+Age+audience))
```

means and SEs

```{r, eval=FALSE}

data %>% group_by(Gender,media) %>% summarise(results=mean(DV)*100,SE=std.error(DV)*100,n=n(),cost=mean(ave.cost.impr),CPR=cost/results) #####skipped updating


```

with Age (emotional much worse with ages 65+)

don't see the effect of emotional being much worse with ages 65+

```{r}
#lm(gwwc_vid_results,DV_costadj~media*Age+Age+audience))


#means and SEs

#print(data %>% group_by(Age,media) %>% summarise(results=mean(DV)*100,SE=std.error(DV)*100,n=n(),cost=mean(ave.cost.impr),CPR=cost/results),n = 50) ###idk how to update this
#print(data %>% group_by(audience,Age,media) %>% summarise(results=mean(DV)*100,SE=std.error(DV)*100,n=n(),cost=mean(ave.cost.impr),CPR=cost/results),n = 500) ###idk how to update this
```

interaction with age and campaign restriction - old people really hated factual long

```{r}
#lm(gwwc_vid_results,DV_costadj~media*agetrin+media*restriction18_39+Age+Gender))
#lm(gwwc_vid_results,DV_costadj~media*agetrin+media*restriction18_39))
```

in just early campaigns

```{r}
#lm(gwwc_vid_results=subset(gwwc_vid_results,restriction18_39==0),DV_costadj~media*agetrin))
```

means and SEs

```{r, eval=FALSE}

gwwc_vid_results %>% filter(restriction18_39 == 0) %>% group_by(Age, media) %>% summarise(
  results = mean(DV) * 100,
  SE = std.error(DV) * 100,
  n = n(),
  cost = mean(ave.cost.impr),
  CPR = cost / results
)



```


